Timeliness of security updates for Android

### 2014-11-10 avostats.tex
Update figures and data for tweaked vulnerability list

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.69\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYear}{$7.7 \pm 1.4$}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.7 \pm 1.0$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \begin{tabular}{l|c|l} Vulnerability & Date known & How known \\ \hline KillingInTheNameOf psneuter ashmem & 2010-07-13 & Fixed on \\ exploid udev & 2010-07-15 & Discovered on \\ RageAgainstTheCage adb & 2010-08-21 & Discovered on \\ levitator & 2011-03-10 & Discovered on \\ Gingerbreak & 2011-04-18 & Fixed on \\ zergRush & 2011-10-06 & Discovered on \\ APK duplicate file & 2013-02-18 & Discovered on \\ APK unchecked name & 2013-06-30 & Discovered on \\ APK unsigned shorts & 2013-07-03 & Fixed on \\ keystore buffer & 2013-09-09 & Discovered on \\ vold asec & 2014-01-27 & Fixed on \\ Fake ID & 2014-04-17 & Fixed on \\ TowelRoot & 2014-05-03 & Discovered on \\\end{tabular} \caption{Root equivalent vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.85\%}
\newcommand{\avoBigExternalMedianVersions}{1.50}
\newcommand{\avoBigExternalMeanVersions}{$2.1 \pm 1.4$}
\newcommand{\avoBigExternalTotalVersions}{58}

>>>>

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.69\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.7 \pm 1.4$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.7 \pm 1.0$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \begin{tabular}{l|c|l} Vulnerability & Date known & How known \\ \hline KillingInTheNameOf psneuter ashmem & 2010-07-13 & Fixed on \\ exploid udev & 2010-07-15 & Discovered on \\ levitator & 2011-03-10 & Discovered on \\ Gingerbreak & 2011-04-18 & Fixed on \\ zergRush & 2011-10-06 & Discovered on \\ APK duplicate file & 2013-02-18 & Discovered on \\ APK unchecked name & 2013-06-30 & Discovered on \\ APK unsigned shorts & 2013-07-03 & Fixed on \\ vold asec & 2014-01-27 & Fixed on \\ Fake ID & 2014-04-17 & Fixed on \\ TowelRoot & 2014-05-03 & Discovered on \\\end{tabular} \caption{Root equivalent vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.85\%}
\newcommand{\avoBigExternalMedianVersions}{1.50}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.1 \pm 1.4$}
\newcommand{\avoBigExternalTotalVersions}{58}

### 2014-11-10 dastats.tex
Update figures and data for tweaked vulnerability list

\newcommand{\daNumDataPoints}{128 Billion}
\newcommand{\daNumStartedApps}{112632}
\newcommand{\daNumInstalledApps}{164685}
\newcommand{\daNumVulnsUsed}{13}

@@

\newcommand{\daNumModels}{2368}

@@

\newcommand{\daOSTotalDaysData}{1127371}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{0.69}
\newcommand{\daUpdatedness}{$0.058 \pm 0.000$}
\newcommand{\daSecurityScore}{$2.7 \pm 0.0$}
\newcommand{\daNumFullVersions}{1128}

@@

\newcommand{\daNumAPIVersions}{14}
\newcommand{\daNumFullVersionUpdates}{4196}
\newcommand{\daNumOSVersionUpdates}{3544}
\newcommand{\daNumFullOnlyVersionUpdates}{632}
\newcommand{\daNumSecurityUpdates}{1353}
\newcommand{\daNumPossibleSecurityUpdates}{1886}
\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline lg & $0.11 \pm 0.00$ & $0.33 \pm 0.00$ & 0.79 & $3.3 \pm 0.0$ \\  motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.82 & $2.9 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.058 \pm 0.000$ & 0.69 & $2.7 \pm 0.0$ \\  samsung & $0.14 \pm 0.00$ & $0.048 \pm 0.000$ & 0.77 & $2.6 \pm 0.0$ \\  htc & $0.14 \pm 0.00$ & $0.088 \pm 0.001$ & 0.95 & $2.5 \pm 0.0$ \\  sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.18 & $2.5 \pm 0.0$ \\  asus & $0.14 \pm 0.00$ & $0.56 \pm 0.01$ & 7.18 & $2.2 \pm 0.0$ \\  symphony & $0.0016 \pm 0.0002$ & $0.042 \pm 0.002$ & 5.73 & $0.15 \pm 0.00$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline Galaxy Nexus & $0.49 \pm 0.00$ & $0.54 \pm 0.01$ & 2.69 & $3.9 \pm 0.0$ \\  Nexus 4 & $0.19 \pm 0.00$ & $0.82 \pm 0.01$ & 7.22 & $3.2 \pm 0.0$ \\  Nexus 7 & $0.17 \pm 0.00$ & $0.74 \pm 0.01$ & 7.08 & $2.9 \pm 0.0$ \\  Desire HD & $0.083 \pm 0.003$ & $0.051 \pm 0.004$ & 0.39 & $2.9 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.69 & $2.9 \pm 0.0$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.0063 \pm 0.0062$ & 2.59 & $1.9 \pm 0.0$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.017 \pm 0.001$ & 2.53 & $1.4 \pm 0.0$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.0006 \pm 0.0036$ & 3.52 & $1.2 \pm 0.0$ \\  GT-P1000 & $0.0096 \pm 0.0009$ & $0.0000 \pm 0.0076$ & 1.73 & $0.94 \pm 0.02$ \\  HTC Desire S & $0.022 \pm 0.001$ & $0.016 \pm 0.004$ & 2.00 & $0.85 \pm 0.01$ \\  GT-I9300 & $0.14 \pm 0.00$ & $0.014 \pm 0.001$ & 7.27 & $0.62 \pm 0.01$ \\  GT-I9505 & $0.0 \pm 0$ & $0.19 \pm 0.00$ & 8.23 & $0.56 \pm 0.01$ \\  GT-N7100 & $0.064 \pm 0.002$ & $0.0011 \pm 0.0058$ & 8.37 & $0.26 \pm 0.02$ \\  HTC Desire HD & $0.0 \pm 0$ & $0.0005 \pm 0.0070$ & 4.05 & $0.10 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline nexus & $0.33 \pm 0.00$ & $0.52 \pm 0.00$ & 1.74 & $3.8 \pm 0.0$ \\  notnexus & $0.12 \pm 0.00$ & $0.041 \pm 0.000$ & 0.69 & $2.6 \pm 0.0$ \\ \end{tabular} \caption{Security scores for summaries} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.8 \pm 0.0\%$}
\newcommand{\daNumOSDevices}{18809}

@@

\newcommand{\daSecScoreBestmodelScore}{$3.9 \pm 0.0$}

@@

\newcommand{\daNumUpdatesUpgrades}{3311}

@@

\newcommand{\daPercUpdatesDowngrades}{4.22\%}

@@

\newcommand{\daEndDate}{2014-10-31}
\newcommand{\daNumOperators}{1392}
\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline o2 uk & $0.24 \pm 0.00$ & $0.12 \pm 0.00$ & 0.41 & $3.7 \pm 0.0$ \\  orange & $0.21 \pm 0.00$ & $0.085 \pm 0.003$ & 0.39 & $3.5 \pm 0.0$ \\  t-mobile & $0.18 \pm 0.00$ & $0.18 \pm 0.00$ & 0.54 & $3.5 \pm 0.0$ \\  sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.4 \pm 0.0$ \\  3 & $0.14 \pm 0.00$ & $0.096 \pm 0.003$ & 0.49 & $3.1 \pm 0.0$ \\  vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.1 \pm 0.0$ \\  at\&t & $0.12 \pm 0.00$ & $0.077 \pm 0.002$ & 0.51 & $3.0 \pm 0.0$ \\  verizon & $0.17 \pm 0.00$ & $0.086 \pm 0.002$ & 0.89 & $2.7 \pm 0.0$ \\  unknown & $0.095 \pm 0.001$ & $0.22 \pm 0.00$ & 1.16 & $2.5 \pm 0.0$ \\  n telenor & $0.023 \pm 0.001$ & $0.10 \pm 0.00$ & 1.59 & $1.4 \pm 0.0$ \\  airtel & $0.067 \pm 0.002$ & $0.029 \pm 0.002$ & 2.00 & $1.1 \pm 0.0$ \\  grameenphone & $0.0080 \pm 0.0005$ & $0.016 \pm 0.001$ & 1.99 & $0.80 \pm 0.00$ \\  banglalink & $0.00016 \pm 0.00011$ & $0.029 \pm 0.002$ & 2.89 & $0.40 \pm 0.01$ \\  robi & $\left(8.5 \pm 8.5\right) \times 10^{-5}$ & $0.042 \pm 0.003$ & 3.33 & $0.33 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.7 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.33 \pm 0.01$}

@@

\newcommand{\daSecScoreBestmodelNumFullVersions}{46}

@@

\newcommand{\daSecScoreBestoperatorNumFullVersions}{87}

@@

\newcommand{\daSecScoreWorstoperatorNumFullVersions}{33}

@@

\newcommand{\daOSCurveFitParamFirst}{86.43}

@@

\newcommand{\daAPICurveFitParamFirst}{110.29}
\newcommand{\daAPICurveFitParamSecond}{\num{0.00316}}

@@

\newcommand{\daAPICurveFullDeployed}{$\left(0.0 \pm 2.3\right) \times 10^{5}$}

@@

\newcommand{\daNumUpdatesBigUpgrades}{776}

@@

\newcommand{\daPercBigUpgrades}{22.45\%}

@@

>>>>

\newcommand{\daNumDataPoints}{153 Billion}
\newcommand{\daNumStartedApps}{121998}
\newcommand{\daNumInstalledApps}{174323}
\newcommand{\daNumVulnsUsed}{11}

@@

\newcommand{\daNumModels}{2374}

@@

\newcommand{\daOSTotalDaysData}{1132105}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{0.64}
\newcommand{\daUpdatedness}{$0.056 \pm 0.000$}
\newcommand{\daSecurityScore}{$2.8 \pm 0.0$}
\newcommand{\daNumFullVersions}{1133}

@@

\newcommand{\daNumAPIVersions}{15}
\newcommand{\daNumFullVersionUpdates}{4209}
\newcommand{\daNumOSVersionUpdates}{3560}
\newcommand{\daNumFullOnlyVersionUpdates}{637}
\newcommand{\daNumSecurityUpdates}{1371}
\newcommand{\daNumPossibleSecurityUpdates}{1887}
\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline lg & $0.11 \pm 0.00$ & $0.32 \pm 0.00$ & 0.79 & $3.3 \pm 0.0$ \\  motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.82 & $2.9 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.056 \pm 0.000$ & 0.68 & $2.7 \pm 0.0$ \\  samsung & $0.14 \pm 0.00$ & $0.047 \pm 0.000$ & 0.76 & $2.6 \pm 0.0$ \\  htc & $0.14 \pm 0.00$ & $0.087 \pm 0.001$ & 0.95 & $2.5 \pm 0.0$ \\  sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.17 & $2.5 \pm 0.0$ \\  asus & $0.14 \pm 0.00$ & $0.56 \pm 0.01$ & 7.18 & $2.2 \pm 0.0$ \\  symphony & $0.0015 \pm 0.0002$ & $0.041 \pm 0.001$ & 5.68 & $0.15 \pm 0.00$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline Galaxy Nexus & $0.49 \pm 0.00$ & $0.53 \pm 0.01$ & 2.66 & $4.0 \pm 0.0$ \\  Nexus 4 & $0.19 \pm 0.00$ & $0.82 \pm 0.01$ & 7.22 & $3.2 \pm 0.0$ \\  Nexus 7 & $0.17 \pm 0.00$ & $0.74 \pm 0.01$ & 7.08 & $2.9 \pm 0.0$ \\  Desire HD & $0.083 \pm 0.003$ & $0.051 \pm 0.004$ & 0.39 & $2.9 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.68 & $2.9 \pm 0.0$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.0063 \pm 0.0062$ & 2.59 & $1.9 \pm 0.0$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.015 \pm 0.001$ & 2.53 & $1.4 \pm 0.0$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.0006 \pm 0.0036$ & 3.52 & $1.2 \pm 0.0$ \\  GT-P1000 & $0.0096 \pm 0.0009$ & $0.0000 \pm 0.0061$ & 1.73 & $0.94 \pm 0.02$ \\  HTC Desire S & $0.022 \pm 0.001$ & $0.016 \pm 0.004$ & 2.00 & $0.85 \pm 0.01$ \\  GT-I9300 & $0.14 \pm 0.00$ & $0.014 \pm 0.001$ & 7.24 & $0.62 \pm 0.01$ \\  GT-I9505 & $0.0 \pm 0$ & $0.18 \pm 0.00$ & 8.15 & $0.55 \pm 0.01$ \\  GT-N7100 & $0.064 \pm 0.002$ & $0.0011 \pm 0.0058$ & 8.37 & $0.26 \pm 0.02$ \\  HTC Desire HD & $0.0 \pm 0$ & $0.0005 \pm 0.0070$ & 4.05 & $0.10 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline nexus & $0.33 \pm 0.00$ & $0.52 \pm 0.00$ & 1.73 & $3.8 \pm 0.0$ \\  notnexus & $0.12 \pm 0.00$ & $0.039 \pm 0.000$ & 0.68 & $2.6 \pm 0.0$ \\ \end{tabular} \caption{Security scores for summaries} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.6 \pm 0.0\%$}
\newcommand{\daNumOSDevices}{18873}

@@

\newcommand{\daSecScoreBestmodelScore}{$4.0 \pm 0.0$}

@@

\newcommand{\daNumUpdatesUpgrades}{3323}

@@

\newcommand{\daPercUpdatesDowngrades}{4.21\%}

@@

\newcommand{\daEndDate}{2014-11-03}
\newcommand{\daNumOperators}{1393}
\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & Security score \\ \hline o2 uk & $0.24 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.8 \pm 0.0$ \\  orange & $0.21 \pm 0.00$ & $0.085 \pm 0.003$ & 0.39 & $3.5 \pm 0.0$ \\  t-mobile & $0.18 \pm 0.00$ & $0.18 \pm 0.00$ & 0.54 & $3.5 \pm 0.0$ \\  sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.4 \pm 0.0$ \\  3 & $0.14 \pm 0.00$ & $0.093 \pm 0.003$ & 0.49 & $3.1 \pm 0.0$ \\  vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.1 \pm 0.0$ \\  at\&t & $0.12 \pm 0.00$ & $0.077 \pm 0.002$ & 0.51 & $3.0 \pm 0.0$ \\  verizon & $0.18 \pm 0.00$ & $0.087 \pm 0.002$ & 0.89 & $2.7 \pm 0.0$ \\  unknown & $0.095 \pm 0.001$ & $0.22 \pm 0.00$ & 1.15 & $2.5 \pm 0.0$ \\  n telenor & $0.023 \pm 0.001$ & $0.10 \pm 0.00$ & 1.57 & $1.4 \pm 0.0$ \\  airtel & $0.066 \pm 0.002$ & $0.028 \pm 0.002$ & 1.89 & $1.1 \pm 0.0$ \\  grameenphone & $0.0078 \pm 0.0005$ & $0.018 \pm 0.001$ & 1.97 & $0.82 \pm 0.00$ \\  banglalink & $0.00016 \pm 0.00011$ & $0.031 \pm 0.002$ & 2.86 & $0.42 \pm 0.01$ \\  robi & $\left(8.4 \pm 8.4\right) \times 10^{-5}$ & $0.040 \pm 0.003$ & 3.17 & $0.36 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.8 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.36 \pm 0.01$}

@@

\newcommand{\daSecScoreBestmodelNumFullVersions}{49}

@@

\newcommand{\daSecScoreBestoperatorNumFullVersions}{88}

@@

\newcommand{\daSecScoreWorstoperatorNumFullVersions}{32}

@@

\newcommand{\daOSCurveFitParamFirst}{87.38}

@@

\newcommand{\daAPICurveFitParamFirst}{109.79}
\newcommand{\daAPICurveFitParamSecond}{\num{0.00315}}

@@

\newcommand{\daAPICurveFullDeployed}{$\left(0.0 \pm 2.4\right) \times 10^{5}$}

@@

\newcommand{\daNumUpdatesBigUpgrades}{778}

@@

\newcommand{\daPercBigUpgrades}{22.43\%}

@@

\newcommand{\daMeanInsecurityPercNominal}{87.21\%}
\newcommand{\daVulnFreeNominal}{0.13}
\newcommand{\daUpdatednessNominal}{0.06}
\newcommand{\daUpdatednessPercNominal}{5.60\%}
\newcommand{\daSecurityScoreNominal}{2.75}
\newcommand{\daUpdatesPerYearNominal}{1.36}
\newcommand{\daOSCurveHalfDeployedNominal}{307.28}
\newcommand{\daOSCurveFullDeployedNominal}{1037.77}
\newcommand{\daAPICurveHalfDeployedNominal}{329.78}
\newcommand{\daAPICurveFullDeployedNominal}{1060.54}
